surfing

### 2021-05-15 inst/surfing.Rmd
GLO

```{r surfing2max, cache=TRUE}
maxp(surfing2)
specificp.gt.test(surfing2,"Brazilian_beachtype",0)
```

```{r profsuppcalcsurfing2, cache=TRUE}
p <- seq(from=0.001,by=0.001,len=10)
l <- profsupp(surfing2,"Brazilian_beachtype",p)
```

```{r}
plot(p,l)
```

@@

```{r,label=savesurfiningingdataset}
save(surfing,surfing_maxp,surfing_table,file="surfing.rda")
```

>>>>

```{r surfing2max, cache=TRUE}
(surfing2_maxp <- maxp(surfing2))
specificp.gt.test(surfing2,"Brazilian_beachtype",0)
```

```{r profsuppcalcsurfing2, cache=TRUE}
p <- seq(from=0.0005,to=0.01,by=0.0005)
l <- profsupp(surfing2,"Brazilian_beachtype",p,relative=FALSE)
l0 <- loglik(indep(surfing_maxp),surfing)
```

```{r}
plot(c(0,p),c(l0,l)-max(l),type='b',xlab="Brazilian beachtype",ylab="support")
```

```{r profsuppcalcsurfing2wide, cache=TRUE}
p_wide <- seq(from=0.002,to=0.04,by=0.002)
l_wide <- profsupp(surfing2,"Brazilian_beachtype",p_wide,relative=FALSE)
```

```{r}
plot(c(0,p_wide),c(l0,l_wide)-max(l),type='b',xlab="Brazilian beachtype",ylab="support")
```

## Generalized log-odds ratios

```{r}
all_Brazilian_surfers <- rownames(surfing_table)[surfing_table$nation == "BRA"]
all_Brazilian_surfers
pnames(surfing2)
pnames(surfing2) %in% all_Brazilian_surfers
table(pnames(surfing2) %in% all_Brazilian_surfers)
Brazilian_surfers <- pnames(surfing2)[pnames(surfing2) %in% all_Brazilian_surfers]
Brazilian_surfers
```

```{r,cache=TRUE}
f <- function(B,...){
  jj <- specificp.test(surfing2, "Brazilian_beachtype", B)
  mp <- jj$null_estimate
  n <- sum(names(mp) %in% all_Brazilian_surfers)
  GLO <- log(mp["Brazilian_beachtype"]^n/prod(mp[which(names(mp) %in% all_Brazilian_surfers)]))
  out <- c(B,GLO, support=jj$null_support)
  names(out) <- c("B","GLO","support")
  return(out)
}
```

```{r calcbrazodr,cache=TRUE}
braz <- c(0.0003,0.0005,0.0008, 0.001,0.002,0.005,0.01,0.02,0.03,0.05)
M <- do.call("rbind",lapply(braz,f))
M[,3] <- M[,3]-max(M[,3])
M
```

```{r}

plot(M[,2],M[,3]-max(M[,3]),type='b')
plot(M[,2],M[,3]-max(M[,3]),type='b',ylim=c(-0.3,0))
```

@@

```{r,label=savesurfiningingdataset}
save(surfing,surfing_maxp,type,surfing_table,file="surfing.rda")
```
